Capstone Movielens Report

### 2025-09-28 reports/capstone-movielens.site/02.6.UMGE-model.Rmd

We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter.

@@

Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.params.fn_tune.test.param_value) parameter.

>>>>

We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) parameter.

@@

Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMG_effect.cv](#func.regularize.test_lambda.UMG_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) parameter.

### 2025-09-28 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd

##### Parameters
\

::: { #func.calc_UMGY_SmoothedDay_effect.params.day_gen_effect .sidebar }
###### ***day_gen_effect***
\
A data frame object representing the _Day General Effect_. It can be returned by the following functions described above:

@@

::: { #func.calc_UMGY_SmoothedDay_effect.details .sidebar }
##### Details
\
Under the hood, the function internally calls the [loess_de](#func.loess_de) described above and constructs the _User+Movie+Genre+Year+(Smoothed)Day (UMGYD) Effect_ data object based on the object of class `loess` it returns along with the data passed by the [day_gen_effect](#func.calc_UMGY_SmoothedDay_effect.params.day_gen_effect) parameter.
:::

@@

::: { #func.train_UMGY_SmoothedDay_effect.params.degree .sidebar }
###### ***degree***
\
A parameter to pass to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.details) section below), meaning the degree of the polynomials to be used.
:::

::: { #func.train_UMGY_SmoothedDay_effect.params.span .sidebar }
###### ***span***
\
A parameter to pass to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.details) section below) to control the degree of smoothing.
:::

@@

This is a helper function that predicts user rating values on the _Test Set_ passed by the [test_set](#func.UMGY_SmoothedDay_effect.predict.params.test_set) parameter, taking into account the _User+Movie+Genre+Year+(Smoothed)Day (UMGYD) Effect_ passed by the [day_smoothed_effect](#func.UMGY_SmoothedDay_effect.predict.params.day_smoothed_effect) parameter.

##### Parameters
\

::: { #func.UMGY_SmoothedDay_effect.predict.params.test_set .sidebar }
###### ***test_set***
\
A _Test Set_ dataset for the _UMGYDE Model_ validation.
:::

::: { #func.UMGY_SmoothedDay_effect.predict.params.day_smoothed_effect .sidebar }
###### ***day_smoothed_effect***
\
A data object representing the _UMGYD Effect_, which can be returned by any of the following functions described above:

@@

The function calculates the _Mean Squared Error (MSE)_ of the _UMGYDE Model_ for the given _Test Set_ passed by the [test_set](#func.calc_UMGY_SmoothedDay_effect.MSE.params.test_set) parameter.

##### Parameters
\

::: { #func.calc_UMGY_SmoothedDay_effect.MSE.params.test_set .sidebar }
###### ***test_set***
\
A _Test Set_ dataset for the _UMGYDE Model_ validation.
:::

::: { #func.calc_UMGY_SmoothedDay_effect.MSE.params.day_smoothed_effect .sidebar }
###### ***day_smoothed_effect***
\
A data object representing the _UMGYD Effect_, which can be returned by any of the following functions described above:

@@

##### Return
\
The _Mean Squared Error (MSE)_ value of the _UMGYDE Model_ computed on the _Test Set_ passed by the [test_set](#func.calc_UMGY_SmoothedDay_effect.MSE.params.test_set) parameter.

@@

The function calculates the _5-Fold Cross Validation MSE_ result for the _UMGYD Effect_ data passed by the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.MSE.cv.params.day_smoothed_effect) parameter.

##### Parameters
\

::: { #func.calc_UMGY_SmoothedDay_effect.MSE.cv.params.day_smoothed_effect .sidebar }
###### ***day_smoothed_effect***
\
A data object representing the _UMGYD Effect_, which can be returned by any of the following functions described above:

@@

The function calculates the _Root Mean Squared Error (RMSE)_ of the _UMGYDE Model_ for the given _Test Set_ passed by the [test_set](#func.calc_UMGY_SmoothedDay_effect.RMSE.params.test_set) parameter.

##### Parameters
\

::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.params.test_set .sidebar }
###### ***test_set***
\
A _Test Set_ dataset for the _UMGYDE Model_ validation.
:::

::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.params.day_smoothed_effect .sidebar }
###### ***day_smoothed_effect***
\
A data object representing the _UMGYD Effect_, which can be returned by any of the following functions described above:

@@

##### Return
\
The _Root Mean Squared Error (RMSE)_ value of the _UMGYDE Model_ computed on the _Test Set_ passed by the [test_set](#func.calc_UMGY_SmoothedDay_effect.RMSE.params.test_set) parameter.

@@

The function calculates the _5-Fold Cross Validation RMSE_ result for the _UMGYD Effect_ data passed by the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv.params.day_smoothed_effect) parameter.

##### Parameters
\

::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.params.day_smoothed_effect .sidebar }
###### ***day_smoothed_effect***
\
A data object representing the _UMGYD Effect_, which can be returned by any of the following functions described above:

@@

##### [train_UMGY_SmoothedDay_effect.RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L171) Function {#func.train_UMGY_SmoothedDay_effect.RMSE.cv}
\
The function is designed to tune the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function's parameters ([degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.degree) and [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.span)), which is ultimately called internally under the hood.

###### Parameters
\

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.degree .sidebar }
  - ***degree:***
A parameter to pass to the internally called [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.details) section below) and, ultimately under the hood, to the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) to specify the degree of the polynomials to be used.

@@

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.span .sidebar }
  - ***span:***
A parameter to pass to the internally called [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.details) section below) and, ultimately under the hood, to the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) to control the degree of smoothing.

@@

##### [train_UMGY_SmoothedDay_effect.RMSE.cv.degree0](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L190) Function {#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0}
\
The overloaded version of the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.degree) parameter value of 0.

###### Parameters
\

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.params.span .sidebar }
  - ***span:***
A parameter to pass to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.details) section below) and, ultimately under the hood, to the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) to control the degree of smoothing.

@@

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.details .sidebar }
###### Details
\
Under the hood, the function internally calls the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.degree) parameter value of 0 and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.span) parameter value taken from the [parameter of the same name](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.params.span) of this function to compute the `RMSE` of the model to be tuned.
:::

@@

###### Return
\
_Root Mean Square Error (RMSE)_ of the _UMGYD_ model trained using the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function called with the given [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.params.span) parameter and the `degree` parameter value equal to 0.

@@

##### [train_UMGY_SmoothedDay_effect.RMSE.cv.degree1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L193) Function {#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1}
\
The overloaded version of the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.degree) parameter value of 1.

###### Parameters
\

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.params.span .sidebar }
  - ***span:***
A parameter to pass to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.details) section below) and, ultimately under the hood, to the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) to control the degree of smoothing.

@@

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.details .sidebar }
###### Details
\
Under the hood, the function internally calls the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.degree) parameter value of 1 and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.span) parameter value taken from the [parameter of the same name](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.params.span) of this function to compute the `RMSE` of the model to be tuned.
:::

@@

###### Return
\
_Root Mean Square Error (RMSE)_ of the _UMGYD_ model trained using the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function called with the given [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.params.span) parameter and the `degree` parameter value equal to 1.

##### [train_UMGY_SmoothedDay_effect.RMSE.cv.degree2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L196) Function {#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2}
\
The overloaded version of the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.degree) parameter value of 2.

###### Parameters
\

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.params.span .sidebar }
  - ***span:***
A parameter to pass to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.details) section below) and, ultimately under the hood, to the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) to control the degree of smoothing.

@@

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.details .sidebar }
###### Details
\
Under the hood, the function internally calls the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.degree) parameter value of 2 and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.params.span) parameter value taken from the [parameter of the same name](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.params.span) of this function to compute the `RMSE` of the model to be tuned.
:::

@@

###### Return
\
_Root Mean Square Error (RMSE)_ of the _UMGYD_ model trained using the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function called with the given [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.params.span) parameter and the `degree` parameter value of 2.

@@

The function is an overloaded version of the [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) function described above, with the fixed values of the [degree](#func.train_UMGY_SmoothedDay_effect.params.degree) and [span](#func.train_UMGY_SmoothedDay_effect.params.span) parameters set to the best values figured out during the tuning process described in the [UMGYDE Model Tuning] section above.

###### Parameters
\

::: { #func.regularize.train_UMGYD_effect.params.train_set .sidebar }
  - ***train_set:***
The _Train Set_ dataset .

@@

::: { #func.regularize.train_UMGYD_effect.params.lambda .sidebar }
  - ***lambda:***
  In accordance with the description in the [UMGYDE Model Regularization: Mathematical Description] section above, this is the _Regularization parameter_ $\lambda$ used for the _UMGYDE Model Regularization_ process.

@@

The function is an overloaded version of the [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) function described above, with the fixed values of the [degree](#func.train_UMGY_SmoothedDay_effect.cv.params.degree) and [span](#func.train_UMGY_SmoothedDay_effect.cv.params.span) parameters set to the best values figured out during the tuning process described in the [UMGYDE Model Tuning] section above.

###### Parameters
\

::: { #func.regularize.train_UMGYD_effect.cv.params.lambda .sidebar }
  - ***lambda:***
  In accordance with the description in the [UMGYDE Model Regularization: Mathematical Description] section above, this is the _Regularization parameter_ $\lambda$ used for the _UMGYDE Model Regularization_ process.

@@

::: { #func.regularize.test_lambda.UMGYD_effect.cv.params.lambda .sidebar }
  - ***lambda:***
  In accordance with the description in the [UMGYDE Model Regularization: Mathematical Description] section above, this is the _Regularization parameter_ $\lambda$ used for the _UMGYDE Model Regularization_ process.

@@

::: { #func.regularize.test_lambda.UMGYD_effect.cv.details .sidebar }
###### Details
\
Under the hood, the function internally calls the [regularize.train_UMGYD_effect.cv](#func.regularize.train_UMGYD_effect.cv) and then [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) described above, and returns the _RMSE_ value that the latter inner function calculates for the given [lambda](#func.regularize.test_lambda.UMGYD_effect.cv.params.lambda) parameter value passed to the former one.
:::

@@

###### Return
\
_Root Mean Squared Error (RMSE)_ of the _UMGYD Model_ trained for the given [lambda](#func.regularize.train_UMGYD_effect.cv.params.span) parameter value.

@@

We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter.

@@

Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.params.fn_tune.test.param_value) parameter.

>>>>

##### Arguments
\

::: { #func.calc_UMGY_SmoothedDay_effect.args.day_gen_effect .sidebar }
###### ***day_gen_effect***
\
A data frame object representing the _Day General Effect_. It can be returned by the following functions described above:

@@

::: { #func.calc_UMGY_SmoothedDay_effect.details .sidebar }
##### Details
\
Under the hood, the function internally calls the [loess_de](#func.loess_de) described above and constructs the _User+Movie+Genre+Year+(Smoothed)Day (UMGYD) Effect_ data object based on the object of class `loess` it returns along with the data passed by the [day_gen_effect](#func.calc_UMGY_SmoothedDay_effect.args.day_gen_effect) parameter.
:::

@@

::: { #func.train_UMGY_SmoothedDay_effect.args.degree .sidebar }
###### ***degree***
\
A parameter to pass to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.details) section below), meaning the degree of the polynomials to be used.
:::

::: { #func.train_UMGY_SmoothedDay_effect.args.span .sidebar }
###### ***span***
\
A parameter to pass to the internally called [calc_UMGY_SmoothedDay_effect](#func.calc_UMGY_SmoothedDay_effect) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.details) section below) to control the degree of smoothing.
:::

@@

This is a helper function that predicts user rating values on the _Test Set_ passed by the [test_set](#func.UMGY_SmoothedDay_effect.predict.args.test_set) parameter, taking into account the _User+Movie+Genre+Year+(Smoothed)Day (UMGYD) Effect_ passed by the [day_smoothed_effect](#func.UMGY_SmoothedDay_effect.predict.args.day_smoothed_effect) parameter.

##### Arguments
\

::: { #func.UMGY_SmoothedDay_effect.predict.args.test_set .sidebar }
###### ***test_set***
\
A _Test Set_ dataset for the _UMGYDE Model_ validation.
:::

::: { #func.UMGY_SmoothedDay_effect.predict.args.day_smoothed_effect .sidebar }
###### ***day_smoothed_effect***
\
A data object representing the _UMGYD Effect_, which can be returned by any of the following functions described above:

@@

The function calculates the _Mean Squared Error (MSE)_ of the _UMGYDE Model_ for the given _Test Set_ passed by the [test_set](#func.calc_UMGY_SmoothedDay_effect.MSE.args.test_set) parameter.

##### Arguments
\

::: { #func.calc_UMGY_SmoothedDay_effect.MSE.args.test_set .sidebar }
###### ***test_set***
\
A _Test Set_ dataset for the _UMGYDE Model_ validation.
:::

::: { #func.calc_UMGY_SmoothedDay_effect.MSE.args.day_smoothed_effect .sidebar }
###### ***day_smoothed_effect***
\
A data object representing the _UMGYD Effect_, which can be returned by any of the following functions described above:

@@

##### Return
\
The _Mean Squared Error (MSE)_ value of the _UMGYDE Model_ computed on the _Test Set_ passed by the [test_set](#func.calc_UMGY_SmoothedDay_effect.MSE.args.test_set) parameter.

@@

The function calculates the _5-Fold Cross Validation MSE_ result for the _UMGYD Effect_ data passed by the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.MSE.cv.args.day_smoothed_effect) parameter.

##### Arguments
\

::: { #func.calc_UMGY_SmoothedDay_effect.MSE.cv.args.day_smoothed_effect .sidebar }
###### ***day_smoothed_effect***
\
A data object representing the _UMGYD Effect_, which can be returned by any of the following functions described above:

@@

The function calculates the _Root Mean Squared Error (RMSE)_ of the _UMGYDE Model_ for the given _Test Set_ passed by the [test_set](#func.calc_UMGY_SmoothedDay_effect.RMSE.args.test_set) parameter.

##### Arguments
\

::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.args.test_set .sidebar }
###### ***test_set***
\
A _Test Set_ dataset for the _UMGYDE Model_ validation.
:::

::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.args.day_smoothed_effect .sidebar }
###### ***day_smoothed_effect***
\
A data object representing the _UMGYD Effect_, which can be returned by any of the following functions described above:

@@

##### Return
\
The _Root Mean Squared Error (RMSE)_ value of the _UMGYDE Model_ computed on the _Test Set_ passed by the [test_set](#func.calc_UMGY_SmoothedDay_effect.RMSE.args.test_set) parameter.

@@

The function calculates the _5-Fold Cross Validation RMSE_ result for the _UMGYD Effect_ data passed by the [day_smoothed_effect](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args.day_smoothed_effect) parameter.

##### Arguments
\

::: { #func.calc_UMGY_SmoothedDay_effect.RMSE.cv.args.day_smoothed_effect .sidebar }
###### ***day_smoothed_effect***
\
A data object representing the _UMGYD Effect_, which can be returned by any of the following functions described above:

@@

##### [train_UMGY_SmoothedDay_effect.RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L171) Function {#func.train_UMGY_SmoothedDay_effect.RMSE.cv}
\
The function is designed to tune the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function's parameters ([degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span)), which is ultimately called internally under the hood.

###### Arguments
\

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree .sidebar }
  - ***degree:***
A parameter to pass to the internally called [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.details) section below) and, ultimately under the hood, to the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) to specify the degree of the polynomials to be used.

@@

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span .sidebar }
  - ***span:***
A parameter to pass to the internally called [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.details) section below) and, ultimately under the hood, to the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) to control the degree of smoothing.

@@

##### [train_UMGY_SmoothedDay_effect.RMSE.cv.degree0](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L190) Function {#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0}
\
The overloaded version of the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) parameter value of 0.

###### Arguments
\

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span .sidebar }
  - ***span:***
A parameter to pass to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.details) section below) and, ultimately under the hood, to the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) to control the degree of smoothing.

@@

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.details .sidebar }
###### Details
\
Under the hood, the function internally calls the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) parameter value of 0 and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) parameter value taken from the [parameter of the same name](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span) of this function to compute the `RMSE` of the model to be tuned.
:::

@@

###### Return
\
_Root Mean Square Error (RMSE)_ of the _UMGYD_ model trained using the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function called with the given [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0.args.span) parameter and the `degree` parameter value equal to 0.

@@

##### [train_UMGY_SmoothedDay_effect.RMSE.cv.degree1](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L193) Function {#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1}
\
The overloaded version of the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) parameter value of 1.

###### Arguments
\

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span .sidebar }
  - ***span:***
A parameter to pass to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.details) section below) and, ultimately under the hood, to the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) to control the degree of smoothing.

@@

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.details .sidebar }
###### Details
\
Under the hood, the function internally calls the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) parameter value of 1 and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) parameter value taken from the [parameter of the same name](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) of this function to compute the `RMSE` of the model to be tuned.
:::

@@

###### Return
\
_Root Mean Square Error (RMSE)_ of the _UMGYD_ model trained using the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function called with the given [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree1.args.span) parameter and the `degree` parameter value equal to 1.

##### [train_UMGY_SmoothedDay_effect.RMSE.cv.degree2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L196) Function {#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2}
\
The overloaded version of the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) parameter value of 2.

###### Arguments
\

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span .sidebar }
  - ***span:***
A parameter to pass to the internally called [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) function (see the [Details](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.details) section below) and, ultimately under the hood, to the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) to control the degree of smoothing.

@@

::: { #func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.details .sidebar }
###### Details
\
Under the hood, the function internally calls the [train_UMGY_SmoothedDay_effect.RMSE.cv](#func.train_UMGY_SmoothedDay_effect.RMSE.cv) described above with the fixed [degree](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.degree) parameter value of 2 and the [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.args.span) parameter value taken from the [parameter of the same name](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) of this function to compute the `RMSE` of the model to be tuned.
:::

@@

###### Return
\
_Root Mean Square Error (RMSE)_ of the _UMGYD_ model trained using the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function called with the given [span](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree2.args.span) parameter and the `degree` parameter value of 2.

@@

The function is an overloaded version of the [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) function described above, with the fixed values of the [degree](#func.train_UMGY_SmoothedDay_effect.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.args.span) parameters set to the best values figured out during the tuning process described in the [UMGYDE Model Tuning] section above.

###### Arguments
\

::: { #func.regularize.train_UMGYD_effect.args.train_set .sidebar }
  - ***train_set:***
The _Train Set_ dataset .

@@

::: { #func.regularize.train_UMGYD_effect.args.lambda .sidebar }
  - ***lambda:***
  In accordance with the description in the [UMGYDE Model Regularization: Mathematical Description] section above, this is the _Regularization parameter_ $\lambda$ used for the _UMGYDE Model Regularization_ process.

@@

The function is an overloaded version of the [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) function described above, with the fixed values of the [degree](#func.train_UMGY_SmoothedDay_effect.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.cv.args.span) parameters set to the best values figured out during the tuning process described in the [UMGYDE Model Tuning] section above.

###### Arguments
\

::: { #func.regularize.train_UMGYD_effect.cv.args.lambda .sidebar }
  - ***lambda:***
  In accordance with the description in the [UMGYDE Model Regularization: Mathematical Description] section above, this is the _Regularization parameter_ $\lambda$ used for the _UMGYDE Model Regularization_ process.

@@

::: { #func.regularize.test_lambda.UMGYD_effect.cv.args.lambda .sidebar }
  - ***lambda:***
  In accordance with the description in the [UMGYDE Model Regularization: Mathematical Description] section above, this is the _Regularization parameter_ $\lambda$ used for the _UMGYDE Model Regularization_ process.

@@

::: { #func.regularize.test_lambda.UMGYD_effect.cv.details .sidebar }
###### Details
\
Under the hood, the function internally calls the [regularize.train_UMGYD_effect.cv](#func.regularize.train_UMGYD_effect.cv) and then [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) described above, and returns the _RMSE_ value that the latter inner function calculates for the given [lambda](#func.regularize.test_lambda.UMGYD_effect.cv.args.lambda) parameter value passed to the former one.
:::

@@

###### Return
\
_Root Mean Squared Error (RMSE)_ of the _UMGYD Model_ trained for the given [lambda](#func.regularize.train_UMGYD_effect.cv.args.span) parameter value.

@@

We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) parameter.

@@

Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report, passing the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) parameter.
